### 2017-05-25 02-02-related.tex
Rename the background/related/sequential files

\subsection{Related Parallelization Work}
\label{sec-related}

We consider related work for both parallelization contributions of this paper: acceleration and scaling
of our MCMC-MMSB algorithm. While acceleration of deep learning algorithms on GPUs
is an ongoing success story, approximative Baysian algorithms are
not such a natural fit for GPUs. Nevertheless, a number of projects explores this terrain.
E.g.~\cite{journals/bioinformatics/MedlarGSBK13} uses GPUs with their
MCMC approach to analyze parental linkage patterns in a biology context and
\cite{DBLP:journals/csda/WhiteP14} does the same to model terrorist activity.
Latent Dirichlet Allocation, another variety of Bayesian Approximation,
is used on GPUs by~\cite{DBLP:conf/nips/YanXQ09}. There is also related
work on the variants of MCMC algorithms that use the gradient to speed
up convergence. Langevin and Hamiltonian dynamics are representatives of
these varieties~\cite{Girolami_riemannmanifold}. Our algorithm uses Riemann
Manifold Langevin dynamics. In \cite{beam2014fast}, GPUs are used to perform
Hamiltonian descent, using Python interfaces to access the standard cuBLAS
library~\cite{cuBLAS}. They limit their optimizations for the GPU to saving
on data transfers between host and device memory. They do not apply their
framework to MMSB.

>>>>

\section{Related Work}
\label{sec-related}

We consider related work for both parts of this paper: acceleration and scaling
of our MCMC-MMSB algorithm. Acceleration of deep learning algorithms on GPUs
is an ongoing success story. Although approximative Baysian algorithms are
not such a natural fit for GPUs, a number of projects explores this terrain.
E.g.~\cite{journals/bioinformatics/MedlarGSBK13} uses GPUs with their
MCMC approach to analyze parental linkage patterns in a biology context and
\cite{DBLP:journals/csda/WhiteP14} does the same to model terrorist activity.
Latent Dirichlet Allocation, another variety of Bayesian Approximation,
is used on GPUs by~\cite{DBLP:conf/nips/YanXQ09}. There is also related
work on the variants of MCMC algorithms that use the gradient to speed
up convergence. Langevin and Hamiltonian dynamics are representatives of
these varieties~\cite{Girolami_riemannmanifold}. Our algorithm uses Riemann
Manifold Langevin dynamics. In \cite{beam2014fast}, GPUs are used to perform
Hamiltonian descent, using Python interfaces to access the standard cuBLAS
library~\cite{cuBLAS}. They limit their optimizations for the GPU to saving
on data transfers between host and device memory. They do not apply their
framework to MMSB.

### 2017-05-25 03-sequential-evaluation.tex
Rename the background/related/sequential files

Due to the performance limitations of the Python implementation, the
experimental configuration of this section is very small.
%
We use the CA-HepPh dataset from the SNAP graph collection, see
Table~\ref{table-snap} in Section~\ref{sec-experimental}. The number of
iterations is~1000;
%Note that these trial runs stop very far before convergence; using a small
%number of
%iterations is valid because the time spent in an iteration does not vary
%during the lifetime of the algorithm.
The number of communities is $K=1024$, the mini-batch size is fixed at $M=32$, the
neighbor sample size $\Neighbors=32$.

@@

A multi-threaded version was created by annotating loops in the
baseline implementation with OpenMP primitives in a straightforward
fashion. This accelerated the stages \textit{update\_phi} and
\textit{update\_pi} with a factor~4 for the very small problem instance
in Table~\ref{table-python-comparison}. For larger problem instances, the
speedup for these dominant phases grew to a factor~10.
% The vectorizing OpenCL
% backend described in the next Section again significantly improves the
% performance, but at the cost of substantial coding effort.
\textbf{\emph{Question: speak about the other stages? they are pipelined.}}

>>>>

Due to the performance limitations of the Python implementation, the
experimental configuration of this section is very small.
%
We use the CA-HepPh dataset from the SNAP graph collection, see
Table~\ref{table-snap} in Section~\ref{sec-experimental}. The number of
iterations is~1000;
%Note that these trial runs stop very far before convergence; using a small
%number of
%iterations is valid because the time spent in an iteration does not vary
%during the lifetime of the algorithm.
the number of communities is $K=1024$, the mini-batch size is fixed at $M=32$, the
neighbor sample size $\Neighbors=32$.

@@

A multi-threaded version was created by annotating loops in the
baseline implementation with OpenMP primitives in a straightforward
fashion. This accelerated the stages \textit{update\_phi} and
\textit{update\_pi} with a factor~4 for the very small problem instance
in Table~\ref{table-python-comparison}. For larger problem instances, the
speedup for these dominant phases grew to a factor~10. The vectorizing OpenCL
backend described in the next Section again significantly improves the
performance, but at the cost of substantial coding effort.
\textbf{\emph{Question: speak about the other stages? they are pipelined.}}
